RadLib: a radiative property model library for CFD

### 2021-07-25 submissions/revision_1/manuscript.tex
revision 1 submitted

%% This list environment is used for the references in the
%% Program Summary
%%
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{float}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{bm}
%\usepackage{seqsplit}
%\usepackage{enumitem}

@@

\newcommand{\BS}{\boldsymbol}
%\setlist[itemize]{noitemsep}%, topsep=0pt}

@@

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, \texttt{lib} containing library files for each interface, \texttt{cmake} with relocatable CMake files for downstream usage, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a}.
\end{itemize}
%
This folder also contains the Python module. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation.

@@

\bibliographystyle{elsarticle-num} 
\bibliography{references}

>>>>

%% This list environment is used for the references in the
%% Program Summary
%%
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{float}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{bm}
%doldb \usepackage{seqsplit}
%doldb \usepackage{enumitem}

@@

\newcommand{\BS}{\boldsymbol}
%doldb\setlist[itemize]{noitemsep}%, topsep=0pt}

@@

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, \texttt{lib} containing library files for each interface, \texttt{cmake} with relocatable CMake files for downstream usage, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
%
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a}.
\end{itemize}
%
This folder also contains the Python module. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation.

@@

%\bibliographystyle{elsarticle-num} 
%\bibliography{references}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Modest_2016}
M.~F. Modest, D.~C. Haworth, {Radiative Heat Transfer In Turbulent Combustion
  Systems: Theory and Applications}, {SpringerBriefs in Applied Sciences and
  Technology}, Springer, 2016.

\bibitem{Modest_2013}
M.~F. Modest, {Radiative Heat Transfer}, third edition Edition, {Academic
  Press}, New York, 2013.

\bibitem{Rothman_2010}
L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{{HITEMP},
  the high-temperature molecular spectroscopic database}}, {Journal of
  Quantitative Spectroscopy {\&} Radiative Transfer} 111~(15) (2010)
  2139--2150.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}

\bibitem{Zhang_2002b}
H.~Zhang, M.~F. Modest, {Evaluation of the Planck-mean absorption coefficients
  from HITRAN and HITEMP databases}, {Journal of Quantitative Spectroscopy {\&}
  Radiative Transfer} 73~(6) (2002) 649--653.
\newblock \href {http://dx.doi.org/10.1016/S0022-4073(01)00178-9}
  {\path{doi:10.1016/S0022-4073(01)00178-9}}.

\bibitem{Hottel_1967}
H.~C. Hottel, A.~F. Sarofim, {Radiative Transfer}, McGraw-Hill, 1967.

\bibitem{Grosshandler_1993}
W.~L. Grosshandler, {{RADCAL}: A Narrow-Band Model for Radiation Calculations
  in a Combustion Environment: NIST technical note 1402}.

\bibitem{TNF}
{TNF Workshop Radiation Models}, \url{https://tnfworkshop.org/radiation/}
  (2021).

\bibitem{Smith_2003}
N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
  \href{https://tnfworkshop.org/radiation/}{{{TNF} Workshop Radiation Models}}
  (2003).
\newline\urlprefix\url{https://tnfworkshop.org/radiation/}

\bibitem{Barlow_2001}
R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, {Scalar profiles and
  {NO} formation in laminar opposed-flow partially premixed methane/air
  flames}, {Combustion and Flame} 127~(3) (2001) 2102--2118.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
  {\path{doi:10.1016/S0010-2180(01)00313-3}}.

\bibitem{Frank_2000}
J.~H. Frank, R.~S. Barlow, C.~Lundquist, {Radiation and nitric oxide formation
  in turbulent non-premixed jet flames}, {Proceedings of the Combustion
  Institute} 28~(1) (2000) 447--454.
\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
  {\path{doi:10.1016/S0082-0784(00)80242-8}}.

\bibitem{Zhu_2002}
X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{{The
  effects of self-absorption of radiation on an opposed flow partially premixed
  flame}}, {Combustion and Flame} 129~(3) (2002) 342--345.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}

\bibitem{Coelho_2002}
P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, {Spectral Radiative Effects and
  Turbulence-Radiation-Interaction in Sandia Flame {D}}, in: {Barlow, Robert
  S., Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), {The
  Proceedings of the Sixth International Workshop on Measurement and
  Computation of Turbulent Nonpremixed Flames}, 2002.

\bibitem{Barlow_1999}
R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{{Nitric
  oxide formation in dilute hydrogen jet flames: isolation of the effects of
  radiation and turbulence-chemistry submodels}}, {Combustion and Flame}
  117~(1-2) (1999) 4--31.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}

\bibitem{Bordbar_2014}
M.~H. Bordbar, G.~Wecel, T.~Hyppanen, {A line by line based weighted sum of
  gray gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
  combustion}, {Combustion and Flame} 161~(9) (2014) 2435--2445.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
  {\path{doi:10.1016/j.combustflame.2014.03.013}}.

\bibitem{Bordbar_2020}
H.~Bordbar, G.~C. Fraga, S.~Hostikka,
  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{{An
  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
  molar fraction ratios in thermal radiation}}, {International Communications
  in Heat and Mass Transfer} 110 (2020) 104400.
\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}

\bibitem{Solovjov_2016}
V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, {The Generalized {SLW}
  Model}, {Journal of Physics: Conference Series} 676 (2016) 1--36.

\bibitem{Solovjov_2017}
V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, {The rank correlated
  {SLW} model of gas radiation in non-uniform media}, {Journal of Quantitative
  Spectroscopy {\&} Radiative Transfer} 197 (2017) 26--44.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.

\bibitem{Badger_2019}
J.~Badger, B.~W. Webb, V.~P. Solovjov, {An exploration of advanced {SLW}
  modeling approaches in comprehensive combustion predictions}, {Combustion
  Science and Technology} 012022~(676) (2019) 1--17.
\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
  {\path{doi:10.1080/00102202.2019.1678907}}.

\bibitem{Coelho_2017}
P.~J. Coelho,
  \href{https://link-springer-com.erl.lib.byu.edu/referenceworkentry/10.1007/978-3-319-32003-8_61-1}{{Radiative
  Transfer in Combustion Systems}}, in: F.~A. Kulacki (Ed.), {Handbook of
  Thermal Science and Engineering}, {Springer International Publishing}, Cham,
  2017, pp. 1--27.
\newblock \href {http://dx.doi.org/10.1007/978-3-319-32003-8{\textunderscore
  }61-1} {\path{doi:10.1007/978-3-319-32003-8{\textunderscore }61-1}}.
\newline\urlprefix\url{https://link-springer-com.erl.lib.byu.edu/referenceworkentry/10.1007/978-3-319-32003-8_61-1}

\bibitem{FDS}
K.~McGrattan, R.~McDermott, C.~Weinschenk, G.~Forney, Fire dynamics simulator,
  technical reference guide, sixth edition (2013-11-04 2013).
\newblock \href {http://dx.doi.org/https://doi.org/10.6028/NIST.sp.1018}
  {\path{doi:https://doi.org/10.6028/NIST.sp.1018}}.

\bibitem{Solovjov_2001}
V.~P. Solovjov, B.~W. Webb, {An Efficient Method for Modeling Radiative
  Transfer in Multicomponent Gas Mixtures With Soot}, {Transactions of the
  ASME} 123 (2001) 450--457.

\bibitem{Solovjov_2001b}
V.~P. Solovjov, B.~W. Webb, {An Efficient Method for Modeling Radiative
  Transfer in Multicomponent Gas Mixtures With Soot}, {Journal of Heat
  Transfer} 123~(3) (2001) 450--457.
\newblock \href {http://dx.doi.org/10.1115/1.1350824}
  {\path{doi:10.1115/1.1350824}}.

\bibitem{Solovjov_2011}
V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, {The {SLW}-1 model for efficient
  prediction of radiative transfer in high temperature gases}, {Journal of
  Quantitative Spectroscopy and Radiative Transfer} 112~(7) (2011) 1205--1212.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.

\bibitem{Solovjov_2020}
V.~P. Solovjov, B.~W. Webb, F.~Andr{\'e}, D.~Lemonnier, {Locally correlated
  {SLW} model for prediction of gas radiation in non-uniform media and its
  relationship to other global methods}, {Journal of Quantitative Spectroscopy
  {\&} Radiative Transfer} 245 (2020) 106857.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2020.106857}
  {\path{doi:10.1016/j.jqsrt.2020.106857}}.

\bibitem{Solovjov_2000}
V.~P. Solovjov, B.~W. Webb, {{SLW} modeling of radiative transfer in
  multicomponent gas mixtures}, {Journal of Quantitative Spectroscopy and
  Radiative Transfer} 65 (2000) 655--672.

\bibitem{Solovjov_2008}
V.~P. Solovjov, B.~W. Webb, {Multilayer modeling of radiative transfer by {SLW}
  and {CW} methods in non-isothermal gaseous medium}, {Journal of Quantitative
  Spectroscopy and Radiative Transfer} 109~(2) (2008) 245--257.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.

\bibitem{Solovjov_2014}
V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, {Extension of the exact {SLW} model
  to non-isothermal gaseous media}, {Journal of Quantitative Spectroscopy and
  Radiative Transfer} 143 (2014) 83--91.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.

\bibitem{Webb_2018}
B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, {An exploration of the influence of
  spectral model parameters on the accuracy of the rank correlated SLW model},
  {Journal of Quantitative Spectroscopy and Radiative Transfer} 218 (2018)
  161--170.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.

\bibitem{Pearson_2014}
J.~T. Pearson, B.~W. Webb, V.~P. Solovjov, J.~Ma, {Efficient representation of
  the absorption line blackbody distribution function for H2O, CO2, and CO at
  variable temperature, mole fraction, and total pressure}, {Journal of
  Quantitative Spectroscopy {\&} Radiative Transfer} 138 (2014) 82--96.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2014.01.019}
  {\path{doi:10.1016/j.jqsrt.2014.01.019}}.

\bibitem{Solovjov_2014b}
V.~P. Solovjov, J.~T. Pearson, \href{https://albdf.byu.edu/}{{ALBDF: Absorption
  Line Blackbody Distribution Function}} (2014).
\newline\urlprefix\url{https://albdf.byu.edu/}

\bibitem{Brewster_1992}
M.~Q. Brewster, {Thermal Radiative Transfer and Properties}, 1992.

\bibitem{Lee_1981}
S.~C. Lee, C.~L. Tien, {Optical constants of soot in hydrocarbon flames},
  {Symposium (International) on Combustion} 18~(1) (1981) 1159--1166.
\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
  {\path{doi:10.1016/S0082-0784(81)80120-8}}.

\bibitem{Stull_1960}
V.~R. Stull, G.~N. Plass, {Emissivity of Dispersed Carbon Particles}, {Journal
  of the Optical Society of America} 50~(2) (1960) 121.
\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
  {\path{doi:10.1364/JOSA.50.000121}}.

\bibitem{Dalzell_1969}
W.~H. Dalzell, A.~F. Sarofim, {Optical Constants of Soot and Their Application
  to Heat-Flux Calculations}, {Journal of Heat Transfer} 91~(1) (1969)
  100--104.
\newblock \href {http://dx.doi.org/10.1115/1.3580063}
  {\path{doi:10.1115/1.3580063}}.

\bibitem{Howarth_1966}
C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), {The Effect of Temperature on
  the Extinction of Radiation By Soot Particles}, Begellhouse, 1966.
\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
  {\path{doi:10.1615/IHTC3.1210}}.

\bibitem{Chang_1990}
H.-c. Chang, T.~T. Charalampopoulos, {Determination of the wavelength
  dependence of refractive indices of flame soot}, {Proceedings of the Royal
  Society of London. Series A: Mathematical and Physical Sciences} 430~(1880)
  (1990) 577--591.
\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
  {\path{doi:10.1098/rspa.1990.0107}}.

\bibitem{Felske_1984}
J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, {Determination of the
  Refractive Indices of Soot Particles from the Reflectivities of Compressed
  Soot Pellets}, {Combustion Science and Technology} 37~(5-6) (1984) 263--283.
\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
  {\path{doi:10.1080/00102208408923757}}.

\bibitem{Williams_2007}
T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, {Measurement of
  the dimensionless extinction coefficient of soot within laminar diffusion
  flames}, {International Journal of Heat and Mass Transfer} 50~(7-8) (2007)
  1616--1630.
\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.

\bibitem{Felske_1977}
J.~D. Felske, C.~L. Tien, {The Use of the Milne-Eddington Absorption
  Coefficient for Radiative Heat Transfer in Combustion Systems}, {Journal of
  Heat Transfer} 99~(3) (1977) 458--465.
\newblock \href {http://dx.doi.org/10.1115/1.3450718}
  {\path{doi:10.1115/1.3450718}}.

\bibitem{Bordbar_personal}
H.~Bordbar, {personal communication RE: WSGG model implementation}.

\bibitem{Chang_1984}
S.~L. Chang, K.~T. Rhee, {Blackbody radiation functions}, {International
  Communications in Heat and Mass Transfer} 11~(5) (1984) 451--455.
\newblock \href {http://dx.doi.org/10.1016/0735-1933(84)90051-4}
  {\path{doi:10.1016/0735-1933(84)90051-4}}.

\end{thebibliography}
